---
title: "Test"
author: "Fred Zenker"
date: '2022-05-25'
output:
  word_document: 
    pandoc_args:
      - --lua-filter=pandoc-ling.lua
  html_document: 
    pandoc_args:
      - --lua-filter=pandoc-ling.lua
  pdf_document: 
    pandoc_args:
      - --lua-filter=pandoc-ling.lua
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(parameters)
library(emmeans)

mod1 <- readRDS('analysis/models/orc_spr_doen_region1_mod.rds')

tab1 <- model_parameters(mod1)

```

## Parameters Table

```{r table, echo = FALSE}

display(tab1)

# https://easystats.github.io/parameters/articles/model_parameters_formatting.html

```

## Linguistic Example

::: ex
This is the most basic structure of a linguistic example. 
:::

:::ex
| Dutch (Germanic)
| Deze zin is in het nederlands.
| DEM sentence AUX in DET dutch.
| This sentence is dutch.
:::

:::ex
| 
| Minci-nun cinan-tal-ey {__/ku-ka} enu chayk-ul pillye-ss-nunci nay-ka kwungkumhayha-nun namca-lul a-n-ta
| Minji-TOP last-month-LOC {__/3MS-NOM} which book-ACC borrow-PST-COMP 1S-NOM wonder-REL man-ACC know-PRES-DEC
| ‘Minji knows the man that I wonder which book {__/he} borrowed last month.’
:::


